### 2023-06-12 manuscript.tex
we have a conclusion! [ci skip]
This build is based on
https://github.com/stain/2022-fdo-paper/commit/36ab554e83d48c8aa533b66d262946c219fd6997.

This commit was created by the following CI build and job:
https://github.com/stain/2022-fdo-paper/commit/36ab554e83d48c8aa533b66d262946c219fd6997/checks
https://github.com/stain/2022-fdo-paper/actions/runs/5244663917

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/fff5377281a23bdf35c2012ec242e6571e1a2692/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/fff5377281a23bdf35c2012ec242e6571e1a2692}{stain/2022-fdo-paper@fff5377}
on June 12, 2023.

>>>>

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/36ab554e83d48c8aa533b66d262946c219fd6997/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/36ab554e83d48c8aa533b66d262946c219fd6997}{stain/2022-fdo-paper@36ab554}
on June 12, 2023.
